---
title: "Eye Tracking"
author: "Blanka Zana"
date: "5 February 2018"
output: html_document
---


 1, data recording (data files (x,y coordinates, pupillary), stimulus files (pictres, onset), auxillary data (EEG or other data collection method, fMRI))
 2, Defining hypothesis
    conceptual
    operational
    
Hypotheses:
1)
C: Visal search patterns are affected by task structure (top-down)
O: - Fixation duration, position (spatial dispersion)
   - Saccades amplitude,amplitude, N, P next
2)
C: More emotionally engaged when involved in interaction (~direction and ostensiveness)
O:- pupil size (time, lighting, in fixations and in saccades?)
  - fixation duration
    

```{r setup, include=FALSE}


pacman::p_load(readr,groupdata2,ggplot2,tidyverse,lmerTest,lme4,MuMIn,data.table,jpeg,grid,tidyr)

# Both experiments are in the same files
setwd("~/Denmark/Study/Semester IV/Eye Tracking/2018 - Eye tracking")
Samples=read_delim('eyetracking_2018_samples.txt',delim='\t')
Fixations=read_delim('eyetracking_2018_fixations.txt',delim='\t')
Saccades=read_delim('eyetracking_2018_saccades.txt',delim='\t')


#1)
#condition = looking/not
#salience = is it or not
model = lmer (pupil_size_fixation ~ time + condition * salience + (1|participant))

#2)
#condition = count/search
model = lmer(saccade_amplitude ~ condition + (1|participant))
```


Loading the clean data V1s


```{r cars}

sac_V1=read.csv2('SaccadesV1.csv',sep = ",")
samp_V1 = read.csv2('SamplesV1.csv',sep = ",")
fix_V1 = read.csv2('FixationsV1.csv', sep = ",")

log1 = read.csv2('./PupilsLogs/logfile_1_2_f.csv',sep = ",")
log2 = read.csv2('./PupilsLogs/logfile_2_1_f.csv',sep = ",")
log3 = read.csv2('./PupilsLogs/logfile_3_2_f.csv',sep = ",")
log4 = read.csv2('./PupilsLogs/logfile_4_1_F.csv',sep = ",")
log5 = read.csv2('./PupilsLogs/logfile_5_2_m.csv',sep = ",")
log6 = read.csv2('./PupilsLogs/logfile_6_1_m.csv',sep = ",")
all_logs = merge(log1, log2, all = T)
all_logs = merge(all_logs, log3, all = T)
all_logs = merge(all_logs, log4, all = T)
all_logs = merge(all_logs, log5, all = T)
all_logs = merge(all_logs, log6, all = T)


setnames(all_logs,"subject","ParticipantID")
colnames(all_logs)[1] <- "Trial"
all_logs$Trial = all_logs$Trial + 1
logs_sac_V1 = merge(all_logs,sac_V1,all = T)
logs_samp_V1 = merge(all_logs,samp_V1, all = T)
logs_fix_V1 = merge(all_logs,fix_V1, all = T)

logs_sac_V1$SearchOrder = as.numeric(logs_sac_V1$SearchOrder)
#logs_sac_V1$Condition = "Search"[logs_sac_V1$Trial < 6[logs_sac_V1$SearchOrder == "1"]

logs_sac_V1$Condition[logs_sac_V1$Trial < 6 & logs_sac_V1$SearchOrder == "1"] = "Search"
logs_sac_V1$Condition[logs_sac_V1$Trial > 6 & logs_sac_V1$SearchOrder == "1"] = "Count"

logs_sac_V1$Condition[logs_sac_V1$Trial < 6 & logs_sac_V1$SearchOrder == "2"] = "Count"
logs_sac_V1$Condition[logs_sac_V1$Trial > 6 & logs_sac_V1$SearchOrder == "2"] = "Search"
#repeat on al V1

logs_samp_V1$Condition[logs_samp_V1$Trial < 6 & logs_samp_V1$SearchOrder == "1"] = "Search"
logs_samp_V1$Condition[logs_samp_V1$Trial > 6 & logs_samp_V1$SearchOrder == "1"] = "Count"

logs_samp_V1$Condition[logs_samp_V1$Trial < 6 & logs_samp_V1$SearchOrder == "2"] = "Count"
logs_samp_V1$Condition[logs_samp_V1$Trial > 6 & logs_samp_V1$SearchOrder == "2"] = "Search"



logs_fix_V1$SearchType[logs_fix_V1$Trial < 6 & logs_fix_V1$SearchOrder == "1"] = "Search"
logs_fix_V1$SearchType[logs_fix_V1$Trial > 6 & logs_fix_V1$SearchOrder == "1"] = "Count"

logs_fix_V1$SearchType[logs_fix_V1$Trial < 6 & logs_fix_V1$SearchOrder == "2"] = "Count"
logs_fix_V1$SearchType[logs_fix_V1$Trial > 6 & logs_fix_V1$SearchOrder == "2"] = "Search"

#why am I always so close yet not there 


logs_sac_V1$DIRECTION [grepl("dir", logs_sac_V1$video)] = "Towards you"
logs_sac_V1$DIRECTION [grepl("div", logs_sac_V1$video)] = "Towards 3rd"

logs_samp_V1$DIRECTION [grepl("dir", logs_samp_V1$video)] = "Towards you"
logs_samp_V1$DIRECTION [grepl("div", logs_samp_V1$video)] = "Towards 3rd"

logs_fix_V1$DIRECTION [grepl("dir", logs_fix_V1$video)] = "Towards you"
logs_fix_V1$DIRECTION [grepl("div", logs_fix_V1$video)] = "Towards 3rd"

#also with ostensiveness

logs_sac_V1$Ostensiveness [grepl("+o", logs_sac_V1$video)] = "Ostensive"
logs_sac_V1$Ostensiveness [grepl("-o", logs_sac_V1$video)] = "Not ostensive"

logs_samp_V1$Ostensiveness [grepl("+o", logs_samp_V1$video)] = "Ostensive"
logs_samp_V1$Ostensiveness [grepl("-o", logs_samp_V1$video)] = "Not ostensive"

logs_fix_V1$Ostensiveness [grepl("+o", logs_fix_V1$video)] = "Ostensive"
logs_fix_V1$Ostensiveness [grepl("-o", logs_fix_V1$video)] = "Not ostensive"


##also with actor gender

logs_sac_V1$ActorGender [grepl("f", logs_sac_V1$video)] = "Female"
logs_sac_V1$ActorGender [grepl("m", logs_sac_V1$video)] = "Male"

logs_samp_V1$ActorGender [grepl("f", logs_samp_V1$video)] = "Female"
logs_samp_V1$ActorGender [grepl("m", logs_samp_V1$video)] = "Male"

logs_fix_V1$ActorGender [grepl("f", logs_fix_V1$video)] = "Female"
logs_fix_V1$ActorGender [grepl("m", logs_fix_V1$video)] = "Male"


############################################################################


```

Creating subsets for the two experiments

```{r}

# fixations by tasks
Visual_fix = subset(logs_fix_V1, Task == "VisualSearch")
Social_fix = subset(logs_fix_V1, Task == "SocialEngagement")

# saccades by tasks
Visual_sac = subset(logs_sac_V1, Task == "VisualSearch")
Social_sac = subset(logs_sac_V1, Task =="SocialEngagement")

#sample by tasks
Visual_samp = subset(logs_samp_V1, Task == "VisualSearch")
Social_samp = subset(logs_samp_V1, Task == "SocialEngagement")


Visual_fix$SearchType = as.factor(Visual_fix$SearchType)
Visual_sac$SearchType = as.factor(Visual_sac$SearchType)
Visual_samp$SearchType = as.factor(Visual_samp$SearchType)

summary(Visual_fix$SearchType == "NA")

```





Visualization 

```{r pressure, echo=FALSE}

#V2 part

ggplot(Visual_fix, aes(Duration, na.rm = T)) + geom_density() + facet_wrap(~SearchType)

ggplot(logs_sac_V1, aes(MeanVelocity)) + geom_histogram() + facet_wrap(~Task)


ggplot(FixV2, aes(PupilSize, fill = ParticipantID)) + geom_density() + facet_wrap(~Task)




dammn = glmer(Duration~SearchType + Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), logs_fix_V1)
summary(dammn)

duck = glmer(Duration~SearchType * Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), logs_fix_V1)
summary(duck)

molly = glmer(Duration~SearchType + (1+SearchType |ParticipantID),family = gaussian (link = log), logs_fix_V1)
summary(molly)

```

duration of fixation
amplitude of saccades
duration of saccades
number of fixations


```{r}
logs_fix_V1 = read.csv("FixationsV2.csv")

#subset first

search = subset(logs_fix_V1,Task == "VisualSearch")
summary(logs_fix_V1$ParticipantGender[unique(logs_fix_V1$ParticipantID)])
search$ParticipantID = as.numeric(as.factor(as.character(search$ParticipantID)))
search$ParticipantID[search$ParticipantGender=="male"]
folds=4

#add column called "folds"
foldyFixV2=fold(search, folds, id_col = "ParticipantID")
summary(foldyFixV2$.folds)


gmod="glmer(Duration~SerachType + Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)"
mod1="glmer(Duration~SearchType * Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)"
mod2="glmer(Duration~SearchType + (1+SearchType |ParticipantID),family = gaussian (link = log), search)"



models=c(gmod,mod1,mod2) 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
cross_v=function(numfolds, data, tempmod_string){
  foldyFixV2=fold(search, folds, id_col = "ParticipantID")
  perf_test_list=c() #Create variables
  perf_train_list=c()
  #r2m=c()
  #r2c=c()

  for(i in seq(numfolds)){
    temp_train = subset(foldyFixV2, .folds != i) #
    temp_test = subset(foldyFixV2, .folds == i) #
    
    temp_model = glmer(Duration~SearchType + Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)
  
    pred_test=predict(temp_model, temp_test, allow.new.levels=T) #
    perf_test=Metrics::rmse(temp_test$Duration, pred_test) #
    perf_test_list=c(perf_test_list, perf_test) #
    pred_train=predict(temp_model, temp_train, allow.new.levels=T) #
    perf_train=Metrics::rmse(temp_train$Duration, pred_train) #
    perf_train_list=c(perf_train_list, perf_train) #
    
    #r2_df = as.data.frame(r.squaredGLMM(temp_model)) 
    #r2m = c(r2m,r2_df[1,1])
    #r2c = c(r2c,r2_df[2,1])
  }
  
    perf_df= data.frame(perf_test_list, perf_train_list, temp_model=tempmod_string)
  
}

for(temp_model in models) 
  if (temp_model == models[1]){
    results_df=cross_v(4, foldyFixV2, temp_model)
   }else{
   results_df = rbind(results_df, cross_v(4, foldyFixV2, temp_model))
  }



###########################

try = results_df
try = data.frame(try)


try = group_by(try, temp_model) %>%
  summarise_each(funs(mean(. , na.rm= T)), perf_test_list)

try = setnames(try,"perf_test_list", "mean_test_rmse" )

#V2 = logs_fix_V1

```


Now we know that the best model is duck (the interaction one), so we run that on the whole data set.

```{r}
duck = glmer(Duration~SearchType * Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), logs_fix_V1)
summary(duck)

plot(resid(duck))




```

Aaaand testing the other hypothesis - saccade amplitudes


```{r}

logs_sac_V1 = read.csv("SaccadesV2.csv")

#subset first

search = subset(logs_sac_V1,Task == "VisualSearch")
summary(logs_fix_V1$ParticipantGender[unique(logs_fix_V1$ParticipantID)])
search$ParticipantID = as.numeric(as.factor(as.character(search$ParticipantID)))
search$ParticipantID[search$ParticipantGender=="male"]
folds=4

#add column called "folds"
foldySacV2=fold(search, folds, id_col = "ParticipantID")
summary(foldySacV2$.folds)


gmod="glmer(Amplitude~SerachType + Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)"
mod1="glmer(Amplitude~SearchType * Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)"
mod2="glmer(Amplitude~SearchType + (1+SearchType |ParticipantID),family = gaussian (link = log), search)"



models=c(gmod,mod1,mod2) 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
cross_v=function(numfolds, data, tempmod_string){
  foldySacV2=fold(search, folds, id_col = "ParticipantID")
  perf_test_list=c() #Create variables
  perf_train_list=c()
  #r2m=c()
  #r2c=c()

  for(i in seq(numfolds)){
    temp_train = subset(foldySacV2, .folds != i) #
    temp_test = subset(foldySacV2, .folds == i) #
    
    temp_model = glmer(Amplitude~SearchType + Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)
  
    pred_test=predict(temp_model, temp_test, allow.new.levels=T) #
    perf_test=Metrics::rmse(temp_test$Duration, pred_test) #
    perf_test_list=c(perf_test_list, perf_test) #
    pred_train=predict(temp_model, temp_train, allow.new.levels=T) #
    perf_train=Metrics::rmse(temp_train$Duration, pred_train) #
    perf_train_list=c(perf_train_list, perf_train) #
    
    #r2_df = as.data.frame(r.squaredGLMM(temp_model)) 
    #r2m = c(r2m,r2_df[1,1])
    #r2c = c(r2c,r2_df[2,1])
  }
  
    perf_df= data.frame(perf_test_list, perf_train_list, temp_model=tempmod_string)
  
}

for(temp_model in models) 
  if (temp_model == models[1]){
    results_df=cross_v(4, foldySacV2, temp_model)
   }else{
   results_df = rbind(results_df, cross_v(4, foldySacV2, temp_model))
  }



###########################

try = results_df
try = data.frame(try)


try = group_by(try, temp_model) %>%
  summarise_each(funs(mean(. , na.rm= T)), perf_test_list)

try = setnames(try,"perf_test_list", "mean_test_rmse" )

```

And the best model for the second hypothesis (Amplitude) is also the interaction one.

```{r}

h2  = glmer(Amplitude~SearchType * Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)

summary(h2)

```

  
  
  

```{r}

FixationsV2 = read.csv('FixationsV2.csv')
jet.colors = colorRampPalette(c("#00007F", "blue","#007FFF","cyan","#7FFF7F","yellow","#FF7F00","red","#7F0000"))

img <- readJPEG('eyetrackingscripts/foraging/ng090ws.jpg')
g = rasterGrob(img,interpolate=TRUE)

#density

a = ggplot(subset(FixationsV2, Task=='VisualSearch' & ParticipantID=='6_3_m2' & Trial==6), aes(x = PositionX, y = PositionY)) +
xlim(0,1920) +
ylim(0, 1080) +
annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + #xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) + 
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans="sqrt")

a


##########################################

fin

FixationsV2 = read.csv('FixationsV2.csv')
jet.colors = colorRampPalette(c("#00007F", "blue","#007FFF","cyan","#7FFF7F","yellow","#FF7F00","red","#7F0000"))

img2 <- readJPEG('eyetrackingscripts/foraging/ng049ws.jpg')
g1 = rasterGrob(img2,interpolate=TRUE)

#density

b = ggplot(subset(FixationsV2, Task=='VisualSearch' & ParticipantID=='3_1_f1' & Trial==3), aes(x = PositionX, y = 1081 -PositionY)) +
xlim(0,1920) +
ylim(0, 1080) +
annotation_custom(g1, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + #xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) + 
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans="sqrt")


##########################################

fin

FixationsV2 = read.csv('FixationsV2.csv')
jet.colors = colorRampPalette(c("#00007F", "blue","#007FFF","cyan","#7FFF7F","yellow","#FF7F00","red","#7F0000"))

img4 <- readJPEG('eyetrackingscripts/foraging/ng049ws.jpg')
g3 = rasterGrob(img4,interpolate=TRUE)

#density

ggplot(subset(FixationsV2, Task=='VisualSearch' & ParticipantID=='2_2_f2' & Trial==3), aes(x = PositionX, y = 1081-PositionY)) +
xlim(0,1920) +
ylim(0, 1080) +
annotation_custom(g3, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + #xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) + 
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans="sqrt")



gridExtra::grid.arrange(a,b,c)

plot(b)
par(new = TRUE)
plot(c)
par(new = T)
plot(d)






FixationsV2 = read.csv('FixationsV2.csv')
jet.colors = colorRampPalette(c("#00007F", "blue","#007FFF","cyan","#7FFF7F","yellow","#FF7F00","red","#7F0000"))

img4 <- readJPEG('eyetrackingscripts/foraging/ng049ws.jpg')
g4 = rasterGrob(img4,interpolate=TRUE)

#density

ggplot(subset(FixationsV2, Task=='VisualSearch' & ParticipantID=='5_1_m2' & Trial==3), aes(x = PositionX, y = 1081-PositionY)) +
xlim(0,1920) +
ylim(0, 1080) +
annotation_custom(g4, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + #xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) + 
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans="sqrt")
d

```




```{r}

img6 <- readJPEG('eyetrackingscripts/foraging/ng021ws.jpg')
g6 = rasterGrob(img6,interpolate=TRUE)

ggplot(subset(FixationsV2, Task=='VisualSearch' & ParticipantID=='1_1_f1' & Trial==1), aes(x = PositionX, y = 1081-PositionY)) +
xlim(0,1920) +
ylim(0, 1080) +
annotation_custom(g6, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + #xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) + 
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans="sqrt")
#SCANPATHS
x = 
ggplot(subset(FixationsV2, Task == 'VisualSearch' & ParticipantID=='1_1_f1' & Trial==1), aes(x=PositionX, y= 1081-PositionY, label=Fixation))  +
annotation_custom(g6, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + 
geom_point(size = 10, alpha = 0.8, color = "magenta") +
geom_path(size = 1, alpha = 0.3) +
geom_text(aes(label = Fixation, size = 5)) 

x

####################3
#Pupil size change over time plot
SamplesV2 = read.csv("SamplesV2.csv")

ggplot(subset(SamplesV2, Task =="SocialEngagement"), aes(TrialTime, PupilSize, colour = Ostension, na.rm = T)) +geom_smooth() + facet_grid(~Directionality)

ggplot(search, aes(Trial,Duration, colour = SearchType, na.rm = T)) + geom_smooth() #facet_grid(~SearchType)
search$ParticipantID = as.numeric(as.factor(as.character(search$ParticipantID)))
search$ParticipantID = as.factor(search$ParticipantID)
ggplot(search, aes(Trial,Duration, colour = ParticipantID, na.rm = T)) + geom_point() + facet_grid(~SearchType)

ggplot(subset(search, ParticipantID=="4"), aes(Stimulus, Duration)) + geom_point()+facet_grid(~SearchType)

ggplot(search,aes(Amplitude,fill = SearchType, colour = SearchType)) + geom_density() + facet_wrap(~SearchType)

search$Trial = as.factor(search$Trial)
ggplot(search, aes(Trial, Amplitude, colour = SearchType)) +geom_smooth() + facet_grid(~Directionality)

```

Social engagament

1) what we wanna look at
  Pupil size ~ Ost + DIR + Time +(1+Ost*DIR|Part)
  
  
  
```{r}
SamplesV2 = read.csv("SamplesV2.csv")

#subset first

social = subset(SamplesV2,Task == "SocialEngagement")
summary(logs_fix_V1$ParticipantGender[unique(logs_fix_V1$ParticipantID)])
social$ParticipantID = as.numeric(as.factor(as.character(search$ParticipantID)))
social$ParticipantID[social$ParticipantGender=="male"]

#in order to be able to feed PupilSize data in a model, outliers need to be removed
ggplot(social,aes(ParticipantID, PupilSize, colour = ParticipantID)) + geom_point()

summary(social$PupilSize)
social = subset(social, PupilSize > 0)


mom = glmer(PupilSize~Ostension * Directionality * Trial + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log), social)
summary(mom)


#using my dataset
summary(Social_fix$ParticipantID)
social$ParticipantID = factor(social$ParticipantID)

dad = glmer(PupilSize~Ostensiveness + DIRECTION + Trial + (1+Ostensiveness + DIRECTION |ParticipantID),family = gaussian (link = log), social)
summary(dad)
#-----------------model aic

model1 = glmer(PupilSize~Ostension + Directionality + Trial + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log), social)
model2 = glmer(PupilSize~Ostension * Directionality * Trial + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log),social)
model3 = glmer(PupilSize~Ostension + Directionality + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log),social)
model4 = glmer(PupilSize~Ostension * Directionality + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log),social)

summary(model1)
summary(model2)
summary(model3)
summary(model4)



#----------------


ggplot(social,aes(Ostension,PupilSize, fill = Directionality)) + geom_bar(stat = "identity") + facet_grid(~Directionality)

#OR since I've been trying to run the model for 10 minutes now, we should argue that pupilsize in fixations dataset is perfectly good to use

FixV2 = read.csv("FixationsV2.csv")
summary(FixV2$ParticipantID)
#subset first

social = subset(FixV2,Task == "SocialEngagement")
summary(FixV2$ParticipantID)
social$ParticipantID = as.numeric(as.factor(as.character(social$ParticipantID)))

b = glmer(PupilSize~Ostension + Directionality + Trial + (1+Directionality |ParticipantID) + (1+Ostension | ParticipantID),family = gaussian (link = log), social)
summary(b)


folds=4

#add column called "folds"
foldysocial=fold(social, folds, id_col = "ParticipantID")
summary(foldySampV2$.folds)


gmod="glmer(PupilSize~Ostension + Directionality + Trial + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log), social)"
mod1="glmer(PupilSize~Ostension * Directionality * Trial + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log),social)"
mod2="glmer(PupilSize~Ostension + Directionality + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log),social)"
mod3="glmer(PupilSize~Ostension * Directionality + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log),social)"


models=c(gmod,mod1,mod2,mod3) 
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
cross_v=function(numfolds, data, tempmod_string){
  foldysocial=fold(social, folds, id_col = "ParticipantID")
  perf_test_list=c() #Create variables
  perf_train_list=c()
  #r2m=c()
  #r2c=c()

  for(i in seq(numfolds)){
    temp_train = subset(foldysocial, .folds != i) #
    temp_test = subset(foldysocial, .folds == i) #
    
    temp_model = glmer(PupilSize~Ostension + Directionality + Trial + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log), social)
  
    pred_test=predict(temp_model, temp_test, allow.new.levels=T) #
    perf_test=Metrics::rmse(temp_test$Duration, pred_test) #
    perf_test_list=c(perf_test_list, perf_test) #
    pred_train=predict(temp_model, temp_train, allow.new.levels=T) #
    perf_train=Metrics::rmse(temp_train$Duration, pred_train) #
    perf_train_list=c(perf_train_list, perf_train) #
    
    #r2_df = as.data.frame(r.squaredGLMM(temp_model)) 
    #r2m = c(r2m,r2_df[1,1])
    #r2c = c(r2c,r2_df[2,1])
  }
  
    perf_df= data.frame(perf_test_list, perf_train_list, temp_model=tempmod_string)
  
}

for(temp_model in models) 
  if (temp_model == models[1]){
    results_df=cross_v(4, foldysocial, temp_model)
   }else{
   results_df = rbind(results_df, cross_v(4, foldysocial, temp_model))
  }



###########################

try = results_df
try = data.frame(try)


try = group_by(try, temp_model) %>%
  summarise_each(funs(mean(. , na.rm= T)), perf_test_list)

try = setnames(try,"perf_test_list", "mean_test_rmse" )





```
  
  

```{r}




```

